Gafo-cc visuals

### 2022-06-04 analysis/gafo-cc-analysis.Rmd
add data

library(tidyverse)
library(brms)
```

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         children = scale(children),
         youngerchildren = scale(youngerchildren),
         touchscreen = factor(touchscreen.x),
        screen = factor(screen))
```

```{r}
bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_null <- brm(abs(clickdistfromtargetcenterx) ~ 1 + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

@@

```{r}
plot(bm_age)

pp_check(bm_age)+xlim(0,2000)

@@

```{r}
bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + screen + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_touch <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + touchscreen + (trialnr|subjid), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))
```

>>>>

library(tidyverse)
library(brms)
library(tidybayes)
```

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         children = scale(children),
         household = scale(household),
         youngerchildren = scale(youngerchildren),
         touchscreen = factor(touchscreen),
        screen = factor(screen))

unique(mdata$community)
```

```{r}
bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid) + (1|community), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_null <- brm(abs(clickdistfromtargetcenterx) ~ 1 + (trialnr|subjid)+ (1|community), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

@@

```{r}
plot(bm_base)

pp_check(bm_base)

@@

```{r}
ps <- bm_base%>%posterior_samples()%>%
  select(starts_with("r_community"))%>%
  pivot_longer(cols = everything(), names_to = "param", values_to = "value")%>%
  filter(grepl("Intercept", param))

ggplot(ps,aes(y = param, x = value)) +
 stat_halfeye(alpha = .7, .width = c(.95, .80)) +
    labs(x = "Posterior estimate", y ="")+
  guides(fill = "none")+
  #geom_vline(xintercept = 0, linetype = "dashed") +
  xlim(-0.2, 0.5)+
  theme_minimal()
```

```{r}
bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx  + (1|subjid) + (screen + children + household|community), 
                              data   = mdata%>%filter(community != "chimfunshi_kumwenda"), 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_touch <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (1|subjid) + (1|community), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

```
```{r}
ps <- bm_screen%>%posterior_samples()%>%
  select(starts_with("r_community"))%>%
  pivot_longer(cols = everything(), names_to = "param", values_to = "value")%>%
  filter(grepl("Intercept", param))

ggplot(ps,aes(y = param, x = value)) +
 stat_halfeye(alpha = .7, .width = c(.95, .80)) +
    labs(x = "Posterior estimate", y ="")+
  guides(fill = "none")+
  #geom_vline(xintercept = 0, linetype = "dashed") +
  xlim(-0.2, 0.5)+
  theme_minimal()
```

### 2022-06-04 analysis/gafo-cc-data-processing.Rmd
add data

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(prettyR) # for describe()
library(jsonlite) # for reading in json files
library(stringr)
library(eeptools)
library(lubridate) # for date handling
library(readxl)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) 
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = as.character(subjID),
         subjID = ifelse(subjID == "VcyYgGQx", "VcyYgFQx", subjID),
         subjID = ifelse(subjID == "R9V7qHrx", "R9v7qHrx", subjID),
         subjID = ifelse(subjID == "QZJvSwfQ","QZJvSwftQ",  subjID),
         subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
         subjID =as.factor(subjID))

@@

tidy_demographics_leipzig <- raw_demographics_leipzig %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, origin = "1899-12-30"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  ) %>%
  select(-c(first_name, last_name, id, test_date, birth_date))%>%
  rename(subjid = code)%>%
  filter(!is.na(ageinyears),
         status == "keep")
```

@@

```{r read_data}
# get all .json files
files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_nigeria <- tibble()
for (f in files) {
  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) 
```

@@

tidy_demographics_nigeria <- raw_demographics_nigeria %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d.%m.%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, `...14`, `...15`, comment))%>%
  rename(subjid = id)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_nigeria <- tidy_demographics_nigeria%>%
  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))
```

@@

data <- bind_rows(
  data_namibia,
  data_leipzig,
  data_nigeria
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

@@

```
```{r}
write_csv(data,"../data/gafo-cc-clean-data.csv")
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(prettyR) # for describe()
library(jsonlite) # for reading in json files
library(stringr)
library(eeptools)
library(lubridate) # for date handling
library(readxl)
library(readODS)

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID = as.character(subjID),
         subjID = ifelse(subjID == "VcyYgGQx", "VcyYgFQx", subjID),
         subjID = ifelse(subjID == "R9V7qHrx", "R9v7qHrx", subjID),
         subjID = ifelse(subjID == "QZJvSwfQ","QZJvSwftQ",  subjID),
         subjID = ifelse(subjID == "TSPeVFYf", "tSPeVFYf", subjID),
         subjID =as.factor(subjID))%>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

tidy_demographics_leipzig <- raw_demographics_leipzig %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  ) %>%
  select(-c(first_name, last_name, id, test_date, birth_date))%>%
  rename(subjid = code)%>%
  filter(!is.na(ageinyears),
         status == "keep")
```

@@

```{r read_data}
# get all .json files
files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_nigeria <- tibble()
for (f in files) {
  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/nigeria/JSONs/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
    subjID = as.character(subjID),
    subjID = ifelse(subjID == "nlger002", "niger002", subjID)
  ) %>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

tidy_demographics_nigeria <- raw_demographics_nigeria %>% 
  filter(community!= "leipzig")%>%
  mutate(
    birth_date = ifelse(birth_date == "10.11.1016", "10.11.2016", birth_date),
    test_date = as.Date(test_date, format = "%d.%m.%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, `...14`, `...15`, comment))%>%
  rename(subjid = id)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_nigeria <- tidy_demographics_nigeria%>%
  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(location = community,
         community = "akure")
```

# Zambia

```{r read_data}
# get all .json files
files <- list.files("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_zambia <- tibble()
for (f in files) {
  jf <- paste("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  raw_data_zambia <- bind_rows(raw_data_zambia, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_zambia <- raw_data_zambia %>%

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) %>%
  select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

```{r demographics}
raw_demographics_zambia <- bind_rows(
  read_ods("../../../../../Cloud/QuantEx/Gafo-cc/data/zambia/gafo-cc-sambia-participants.ods", sheet = 1)
  )

tidy_demographics_zambia <- raw_demographics_zambia %>% 
  filter(community!= "leipzig")%>%
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
  rename(subjid = id)%>%
  filter(!is.na(ageinyears))
```

```{r}
data_zambia <- tidy_demographics_zambia%>%
  left_join(tidy_data_zambia%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "chimfunshi_kumwenda")
```

@@

data <- bind_rows(
  data_namibia,
  data_leipzig,
  data_nigeria,
  data_zambia
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

@@

```{r}
write_csv(data,"../data/gafo-cc-clean-data.csv")
```

### 2022-06-04 analysis/gafo-cc-visuals.Rmd
add data

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "lm")+
  scale_color_colorblind()+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()

@@

ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .2))+
  labs(x = "Binned target position", y = "Mean imprecision")+
  #ylim(0,1000)+
  theme_minimal()
```

>>>>

```{r}
data%>%
  group_by(community)%>%
  summarise(n= n_distinct(subjid))
```

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  scale_color_colorblind()+
  ylim(0,1000)+
  labs(x = "Age (in years)", y ="Imprecision")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()

@@

ggplot(ptp, aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "Binned target position", y = "Mean imprecision")+
  scale_color_colorblind()+
  #ylim(0,1000)+
  theme_minimal()
```
